Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-23 man/figures/std_anomalies.Rmd
update figures std anomalies and EVI profile

---
output: 
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    highlight: null
    reference_docx: ../../templates/template_pagebreak.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, dpi = 200)
```

```{r}
library("tidyverse")
library("here")
library("dplyr")
library("ggrepel")
library("scales")

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
```

```{r, echo=FALSE}
show_text <- FALSE
```

@@

```{r, eval=FALSE}
iv <- read.csv(here("data/evi", "iv_composite.csv"), header = TRUE, sep = ',')

drought_years <- c(2005, 2012)

evi_profile_dat_ref <- iv %>% 
  filter(!year %in% drought_years) %>% 
  group_by(composite) %>% 
  dplyr::summarise(mean=mean(evi, na.rm=TRUE),
            sd = sd(evi, na.rm=TRUE),
            se = sd/sqrt(length(evi))) %>% 
  mutate(composite_dates = 
           plyr::mapvalues(composite,
                           c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23),
                           c('01-01','01-17','02-02','02-18','03-06','03-22','04-07','04-23',
                             '05-09','05-25','06-10','06-26','07-12','07-28','08-13','08-29',
                             '09-14','09-30','10-16','11-01','11-17','12-03','12-19'))) %>%
  mutate(cd = as.Date(composite_dates, format = '%m-%d')) %>% 
  mutate(period = 'reference')

evi_profile_dat_2005 <- iv %>% 
  filter(year == 2005) %>% 
  group_by(composite) %>% 
  dplyr::summarise(mean=mean(evi, na.rm=TRUE),
            sd = sd(evi, na.rm=TRUE),
            se = sd/sqrt(length(evi))) %>% 
  mutate(composite_dates = 
           plyr::mapvalues(composite,
                           c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23),
                           c('01-01','01-17','02-02','02-18','03-06','03-22','04-07','04-23',
                             '05-09','05-25','06-10','06-26','07-12','07-28','08-13','08-29',
                             '09-14','09-30','10-16','11-01','11-17','12-03','12-19'))) %>%
  mutate(cd = as.Date(composite_dates, format = '%m-%d')) %>% 
  mutate(period = '2005')

evi_profile_dat_2012 <- iv %>% 
  filter(year == 2012) %>% 
  group_by(composite) %>% 
  dplyr::summarise(mean=mean(evi, na.rm=TRUE),
            sd = sd(evi, na.rm=TRUE),
            se = sd/sqrt(length(evi))) %>% 
  mutate(composite_dates = 
           plyr::mapvalues(composite,
                           c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23),
                           c('01-01','01-17','02-02','02-18','03-06','03-22','04-07','04-23',
                             '05-09','05-25','06-10','06-26','07-12','07-28','08-13','08-29',
                             '09-14','09-30','10-16','11-01','11-17','12-03','12-19'))) %>%
  mutate(cd = as.Date(composite_dates, format = '%m-%d')) %>% 
  mutate(period = '2012')

# Join the three dataframes
evi_profile_compara_dat <- rbind(evi_profile_dat_ref, evi_profile_dat_2005, evi_profile_dat_2012)

# colref <- '#455883'
# colref2 <- '#10253F'
# col2005 <- '#00BA38'
# col2012 <- '#F8766D'

col2012 <- '#0700fe'
col2005 <- '#19e00b'
colref <- '#7b7b7b'

profile_compara <- ggplot(evi_profile_compara_dat, aes(cd, y=mean, color=period)) + 
  geom_errorbar(aes(ymin = mean - 2*se, ymax= mean + 2*se), width=3, size=.5) + 
  #geom_errorbar(aes(ymin = mean - sd, ymax= mean + sd), width=4, colour='black') + 
  geom_line(size=.9) + 
  geom_point(size=1.5, fill='white', shape=21) +
  scale_x_date(labels = function(x) format(x, "%b"),
               breaks = date_breaks('month')) + 
  ylab('EVI') + xlab('Date') + 
  theme_bw() +
  theme_classic() + 
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        legend.position = c(0.1,.9),
        plot.title = element_text(hjust = -0.05, size = 16, 
                                    margin = margin(t=-5, b=1))) +
  scale_color_manual(values=c(col2005, col2012, colref))

profile_compara 
```

```{r}
# From explore_anomalies.Rmd 
# Read data 
anomalias_evimean <- read.csv(here("data/anomalies", "anomalias_evimean.csv"),header = TRUE, sep = ',')

@@

# colours 
color_neg <- '#a63603'
color_pos <- '#006d2c'

# Standardized Anomalies 
avg_sa_clu <- anomalias_evimean %>% 
  group_by(clu_pop2, y) %>% 
  dplyr::summarise(mean=mean(sa, na.rm=T),
            sd = sd(sa, na.rm=T),
            se = sd/sqrt(length(sa))) %>% 
 mutate(signo = ifelse(mean >= 0, 'pos', 'neg'))

@@

plot_sa_clu  <- avg_sa_clu %>%  
  ggplot(aes(x=y, y=mean, fill=signo)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se, colour=signo), width=.5) +
  facet_wrap(~clu_pop2, nrow = 2) + 
  scale_fill_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  scale_color_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  ylab(myylab) + xlab('') +
  theme_bw() +
  theme(text = element_text(size=12),
        legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = -0.05, size = 12, 
                                    margin = margin(t=-5, b=1)))

# plot_sa_clu
```

```{r, fig.height=9} 
# grid.arrange(profile_compara, plot_sa_clu)
```

```{r, fig.height=7, eval=FALSE}
a_profile_compara <- profile_compara + labs(title = "a")
b_plot_sa_clu <- plot_sa_clu + labs(title = "b")
a_profile_compara + b_plot_sa_clu + plot_layout(ncol=1)
```

```{r, fig.width=3.5, fig.height=5, fig.asp = .8}
plot_sa_clu 
```

>>>>

---
output:
  word_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r load_pkg}
library("tidyverse")
library("here")
library("scales")
library("patchwork")
```

@@

```{r data}
# From explore_anomalies.Rmd 
# Read data 
anomalias_evimean <- read.csv(here("data/anomalies", "anomalias_evimean.csv"),header = TRUE, sep = ',')

@@

# Standardized Anomalies 
avg_sa_clu <- anomalias_evimean %>% 
  group_by(clu_pop2, y) %>% 
  dplyr::summarise(mean=mean(sa, na.rm=T),
            sd = sd(sa, na.rm=T),
            se = sd/sqrt(length(sa))) %>% 
 mutate(signo = ifelse(mean >= 0, 'pos', 'neg'))
```

```{r plot}
# colours 
color_neg <- '#a63603'
color_pos <- '#006d2c'

@@

plot_sa_clu  <- avg_sa_clu %>%  
  ggplot(aes(x=y, y=mean, fill=signo)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se, colour=signo), width=.5) +
  facet_wrap(~clu_pop2, nrow = 2) + 
  scale_fill_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  scale_color_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  ylab(myylab) + xlab('') +
  theme_bw() +
  theme(text = element_text(size=12),
        legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = -0.05, size = 12, 
                                    margin = margin(t=-5, b=1)))
```

```{r out_plot, fig.width= 4, dpi = 300, out.width = 0.8}
plot_sa_clu 
```

```{r oldFigure, eval=FALSE, fig.height=7}
## See profile_EVI.Rmd 
# grid.arrange(profile_compara, plot_sa_clu)

a_profile_compara <- profile_compara + labs(title = "a")
b_plot_sa_clu <- plot_sa_clu + labs(title = "b")
a_profile_compara + b_plot_sa_clu + plot_layout(ncol=1)
```
